---
title: "wranglingI"
output: html_document
---


```{r}
library(pacman)
p_load(rio, tidyr, tidyverse, tidytext, gt, dplyr, ggplot2, wordcloud, tokenizers, tidytext, textdata, RColorBrewer, knitr, lubridate)

```


library(ldatuning)
```{r}
df <- import("wte_data_complete_2021-09-22.xlsx")
```


##Lower cases
```{r}
df_lower <- df %>% 
  mutate(text = tolower(text)) %>%
  mutate(thread_title = tolower(thread_title))
```

# Replace
```{r}
df_lower$text<- str_replace_all(df_lower$text, "wks", "weeks") %>%
  str_replace_all("ftm", "first_time_mom") %>%
  str_replace_all("gd", "gestational_diabetes") %>%
  str_replace_all("gestation diabetes", "gestational_diabetes") %>%
  str_replace_all("hbp", "high_bp") %>%
  str_replace_all("pree", "preeclampsia") %>%
  str_replace_all("pre-e", "preeclampsia") %>%
  str_replace_all("c section", "c-section") %>%
  str_replace_all("c- section", "c-section") %>%
  str_replace_all("csection", "c-section") %>%
  str_replace_all("bp", "blood_pressure") %>%
  str_replace_all("stm", "second_time_mom") %>%
  str_replace_all("hg", "hyperemesis_gravidarum") %>%
  str_replace_all("bfp", "big_fat_positive") %>%
  str_replace_all("u/s", "ultrasound") %>%
  str_replace_all("sono", "ultrasound") %>%
  str_replace_all("ultrasounds", "ultrasound") %>%
  str_replace_all("edd", "estimated_delivery_date") %>%  
  str_replace_all("ttc", "trying_to_conceive") %>% 
  str_replace_all("’", "'") %>%
  str_replace_all("lbs", "pounds")
```
#removed "hb" (heart beat) --> issues with hbp; removed str_replace_all("ob", "obgyn")


## Clarifying with Dr. Lars

full terms --> abbrebiation to catch in the topic modeling? 
or gestional diabetes --> gd so defferentiate from diabetes
  str_replace_all("w", "weeks") %>%
  str_replace_all("weeks", "week") %>%
  str_replace_all("days", "day") %>%
  str_replace_all("bumps", "bump") %>%
  str_replace_all("pregnancy", "pregnant") %>%
  str_replace_all("feel", "feeling") %>%
  str_replace_all("lbs", "pounds") %>%
  str_replace_all("dr", "doctor") %>%
  str_replace_all("doctors", "doctor") %>%
  str_replace_all("pregnancy", "pregnant") 

##Tokenization
```{r}
df_tokens <-  df_lower %>%
  unnest_tokens(word, text)
```

```{r}
df_tokens %>% 
  count(word, sort = T) %>%
  slice_max(n, n = 10)
```


# Removing digits and common words by adding them to stop words #

```{r}
final_stop <- 
  data.frame(
    word = c("im", "ive", "dont", "off", "and", "doesnt", "ill", "havent", "wont", "didnt", "i'm", "it's", "don't"), 
    lexicon = "custom") %>%
  rbind(stop_words)
```

# Tokenizing #
```{r}
df_tokens  <- df_tokens %>% 
  anti_join(final_stop)
```


```{r}
head(df_tokens$word, 10)
```



```{r}
df_tokens %>%
  count(word, sort = TRUE)
```

## Remove any words that consist only of numerals. 

```{r}
df_tokens <- 
  df_tokens %>% 
  filter(str_detect(word, "[a-z]"))
```

## Frequently Used Words

```{r}
df_tokens %>%
  count(word, sort = TRUE) %>% 
  with(wordcloud(word, n, max.words = 90)) 
```

```{r}
get_sentiments("bing") %>% 
  filter(word == "sharp")
```
## Sentiment analysis with inner join
```{r}
head(df_tokens)
```

## Bing_Negative
```{r}
bing_neg <- get_sentiments("bing") %>%
  filter(!word=="bump", sentiment == "negative") %>% 
  filter(!word=="bumps", sentiment == "negative") %>%     
  filter(!word=="skinny", sentiment == "negative")

  # Non-positive terms: tops, lean (leaning vs. lean protein), defeated (negative, why under positive sentiment?)

```


## Bing_Positive
```{r}
bing_pos <- get_sentiments("bing") %>%
  filter(sentiment == "positive")
bing_pos
```

## How to select random sample
```{r}
df_lower %>% 
  filter(str_detect(text, "bump")) %>% 
  slice_sample(n=50) %>% 
  pull(text)
## to make sure bump is used to describe pregnant belly (neutral)
```

```{r}
df_lower %>% 
  filter(str_detect(text, "bumps")) %>% 
  slice_sample(n=50) %>% 
  pull(text)
```

```{r}
df_lower %>% 
  filter(str_detect(text, "skinny")) %>% 
  slice_sample(n=50) %>% 
  pull(text)
```
 
## Negative terms: bloated, swollen, hangs, funny, joke

## Non-Negative terms: bumps, bump, skinny

## Does "cheap" have negative meanings?  "cheaper" was in bing_postive
```{r}
df_lower %>% 
  filter(str_detect(text, "cheap")) %>% 
  slice_sample(n=50) %>% 
  pull(text)
```
```{r}
df_lower %>% 
  filter(str_detect(text, "slowly")) %>% 
  slice_sample(n=50) %>% 
  pull(text)
```
# Positive terms: tops, sharp, lean, cheaper, boom,  defeated?

# Non-positive terms: tops, lean (leaning vs. lean protein), defeated (negative, why under positive sentiment?), sharp (negative meaning)
```{r}
df_lower %>% 
  filter(str_detect(text, "sharp")) %>% 
  slice_sample(n=50) %>% 
  pull(text)
```

```{r}
bing_neg_r <- get_sentiments("bing") %>%
  filter(!word=="bump", sentiment == "negative") %>% 
  filter(!word=="bumps", sentiment == "negative") %>%     
  filter(!word=="skinny", sentiment == "negative") 
bing_pos_r <- get_sentiments("bing") %>%
  filter(!word=="tops", sentiment == "positive") %>%   
  filter(!word=="lean", sentiment == "positive") %>%   
  filter(!word=="defeated", sentiment == "positive")
```


## Bing_neg w/o "Bump"
```{r}
df_tokens %>% 
  inner_join(bing_neg_r) %>% 
  count(word, sort = TRUE)
```
## Bing_pos 
```{r}
df_tokens %>% 
  inner_join(bing_pos_r) %>% 
  count(word, sort = TRUE)
```


```{r}
get_sentiments("bing")
bing_all <- 
  get_sentiments("bing") %>% 
  filter(!word=="bump") %>% 
  filter(!word=="bumps") %>% 
  filter(!word=="skinny") %>% 
  filter(!word=="tops") %>%   
  filter(!word=="lean") %>%   
  filter(!word=="defeated")
```

```{r}
df_sentiment <- df_tokens %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word, sentiment, sort = TRUE) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

df_sentiment
```


```{r}
df_tokens <- 
  df_tokens %>% 
  mutate(
    date_2weeks = date %>%
      cut(breaks = "2 weeks") %>% 
      as.Date(),
    date_weekly = date %>% 
      cut(breaks = "1 week") %>% 
      as.Date()
    )

df_tokens
```

## Weekly
```{r}
# df_tokens$month <- floor_date(df_tokens$date, "month")

df_sent <- 
  df_tokens %>% 
  inner_join(bing_all) %>% 
  count(date_weekly, sentiment) %>% 
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

df_sent
```



```{r}
p_sent_line <- 
  ggplot(df_sent, aes(date_weekly, sentiment)) + 
  geom_line(show.legend = FALSE) 

p_sent_line
```


```{r}
p_sent_smooth <- 
  ggplot(df_sent, 
         aes(date_weekly, sentiment)) + 
  geom_smooth(show.legend = FALSE,
              span = 0.12,
              se = F,
              color = "black") +
  theme_light()

p_sent_smooth
```


## Biweekly
```{r}
df_sent_2wks <- 
  df_tokens %>% 
  inner_join(bing_all) %>% 
  count(date_2weeks, sentiment) %>% 
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

df_sent_2wks
```

```{r}
p_sent_line_2wks <- 
  ggplot(df_sent_2wks, aes(date_2weeks, sentiment)) + 
  geom_line(show.legend = FALSE) 

p_sent_line_2wks

p_sent_smooth_2wks <- 
  ggplot(df_sent_2wks, 
         aes(date_2weeks, sentiment)) + 
  geom_smooth(show.legend = FALSE,
              span = 0.12,
              se = F,
              color = "black") +
  theme_light()

p_sent_smooth_2wks
```


## look at the data by 2 wks timeline -- function

## biwkly or using span --> credible 
## line_geom with 2weeks/wkly
## smooth

# How can we conclude here? 
```{r}

```

# Next step? n-gram? 

# topic modeling? 


